\cvsection{Work experience}

\cvevent{\textbf{Machine Learning Specialist}}{\href{https://www.adalisk.com/?lang=en}{Adalisk}}{April 2021 -- present}{Tbilisi, Georgia}

Engaged in research in the field of application of computer vision in dentistry for \href{https://glidewelldental.com/}{GlidewellDental}. Responsible for developing new approaches to improve work with 2D images, 3D images, point clouds, and meshes

\begin{itemize}
	\item Developed a teeth mesh segmentation and classification system using PyTorch and PyTorch Geometric.
	\item Developed an internal framework for working with graph data using PyTorch and PyTorch Geometric.
\end{itemize}

\divider

\cvevent{\textbf{Computer Vision Engineer}}{\href{https://mipt.ru/}{
Moscow Institute of Physics and Technology (MIPT)}}{November 2018 -- April 2021}{MIPT, Dolgoprudny, Russia}

Engaged in the development of ML-based systems for recognizing objects on large-scale geo-images.

\begin{itemize}
	\item Developed a system for anomaly detection on large images of the earth's surface, using an unsupervised learning approach.
	\item Investigated the possibility of applying L0 regularization-based algorithms for infrared video denoising.
	\item Developed a system for stitching many small photographs of the earth into a single continuous canvas.
\end{itemize}

\divider


\cvevent{\textbf{Intern risk analyst}}{\href{www.tinkoff.ru}{Tinkoff Bank}}{August 2018 -- November 2018}{Moscow, Russia}

Engaged in improving ML algorithms for calculating insurance risks in the insurance department.

\begin{itemize}
	\item Improved the system for calculating insurance risks in car insurance.
\end{itemize}

%\divider

